The Impact of Malaria Episodes and Treatment Regimens on Adverse Pregnancy Outcomes in Ugandan Women

### 2025-03-30 products/manuscript/Manuscript.qmd
upd

library(here)             # Manage file paths
library(tidyverse)        # Core data wrangling: includes dplyr, ggplot2, readr, forcats, lubridate
library(janitor)          # Cleaning column names
library(skimr)            # Quick data summary
library(gtsummary)        # Creating summary tables
library(gt)               # Formatting tables
library(knitr)            # Table formatting
library(kableExtra)       # Additional table customization
library(ggpubr)           # Publication-ready plots
library(Amelia)           # Missing data visualization
library(pwr)              # Power analysis
library(DiagrammeR)       # Flowcharts/Diagrams
library(survival)         # Survival analysis
library(survminer)        # Survival plots

@@

# Load required packages
library(tibble)
library(knitr)
library(kableExtra)

>>>>

library(here)             # Manage file paths
library(tidyverse)        # Core data wrangling: includes dplyr, ggplot2, readr, forcats, lubridate
library(janitor)          # Cleaning column names
library(skimr)            # Quick data summary
library(gtsummary)        # Creating summary tables
library(gt)               # Formatting tables
library(knitr)            # Table formatting
library(kableExtra)       # Additional table customization
library(ggpubr)           # Publication-ready plots
library(Amelia)           # Missing data visualization
library(pwr)              # Power analysis
library(DiagrammeR)       # Flowcharts/Diagrams
library(survival)         # Survival analysis
library(survminer)        # Survival plots
library(flextable)
library(webshot2)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
